Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-19 paper/structureScene.tex
finish Vincent's biography

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/lostanlen}}]{Vincent Lostanlen} was born in 1992. He received an engineering degree from TELECOM ParisTech in 2013 and M.S. degree in acoustics, signal processing, and musical informatics (ATIAM) from the Universit\'{e} Pierre et Marie Curie and the Ircam (UPMC) in Paris, France, in 2013. Since 2013, he is a Ph.D. student at \'{E}cole normale sup\'{e}rieure in Paris, working under the supervision of St\'{e}phane Mallat.
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/lostanlen}}]{Vincent Lostanlen} was born in 1992. He received an engineering degree from TELECOM ParisTech in 2013 and his M.S. degree in acoustics, signal processing, and musical informatics (ATIAM) from the Universit\'{e} Pierre et Marie Curie (UPMC) and the Ircam in Paris, France, in 2013. Since 2013, he is a Ph.D. student at \'{E}cole normale sup\'{e}rieure in Paris, working under the supervision of St\'{e}phane Mallat. His research focuses on defining convolutional operators in the time-frequency domain with applications in audio classification.
\end{IEEEbiography}
